Supermassive black holes and their host spheroids \\ III. Mbh-n paper

### 2015-11-18 papers/ellicular/ellicular.tex
victory

Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution. }

@@

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Section, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
are small for these two galaxies. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in Savorgnan \& Graham (2015).
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in the {\bf central fast rotator} NGC 3115 
{\bf (e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) }
is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies (e.g.~\citealt{michardmarchal1993}).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

>>>>

Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution.

@@

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Section, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in \cite{paperI}.
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
are small for these two galaxies. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in \cite{paperI}.
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in the central fast rotator NGC 3115 
(e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) 
is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies (e.g.~\citealt{michardmarchal1993}).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

### 2015-11-18 papers/mbhn/mbhn.tex
victory

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component $n_{\rm sph}$ has been shown to tightly correlate 
with the mass of the central supermassive black hole $M_{\rm BH}$ by some studies. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known galaxy scaling relations: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ relations, 
where $L_{\rm sph}$ indicates the galaxy's spheroid luminosity. 
However, it is widely recognized that obtaining an accurate estimate of the spheroid S\'ersic index is a challenging task, 
and -- not surprisingly -- other studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other correlations between the black hole mass and various galaxy properties, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
This sample is the largest to date used to investigate black hole mass scaling relations. 
In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite in a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(Y|X)} \simeq 0.25 \rm~dex$). 
{\bf to be finished...}
\end{abstract}

@@

of the light distribution of the stellar spheroidal and disk components of galaxies (add REFS), 

@@

we performed state-of-the-art modelling for the largest sample of galaxies to date (Savorgnan \& Graham 2015, hereafter \emph{Paper I}),  

@@

In Savorgnan et al.~(2015, hereafter \emph{Paper II}) we examined the correlations between black hole mass and 
galaxy luminosity, spheroid luminosity and spheroid stellar mass. 

@@

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
Savorgnan \& Graham (2015) explain that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices have been estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes which report only the statistical errors 
associated with their fitted parameters. 
Refer to \emph{Paper I} for a detailed discussion on this. }.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as mergers are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
\label{sec:anal}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the S0 galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis.

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{graham2013review} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{graham2013review} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
It is also worth mentioning that, 
although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram with our high-quality dataset  
derived from state-of-the-art multicomponent decompositions, 
that were performed in a consistent manner 
and using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{graham2013review} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
{\bf why?? dust? multicomponent? classification?}

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevents us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we find that 
early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.50 \bigr) . 
\end{equation*}
\\

>>>>

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
with the mass of the central supermassive black hole, $M_{\rm BH}$. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$, 
where $L_{\rm sph}$ indicates the galaxy's spheroid luminosity. 
However, it is widely recognized that obtaining an accurate estimate of the spheroid S\'ersic index is a challenging task, 
and -- not surprisingly -- some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other black hole mass scaling relations, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite in a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(Y|X)} \simeq 0.25 \rm~dex$). 
{\bf to be finished...}
\end{abstract}

@@

of the light distribution of the stellar spheroidal\footnote{Throughout the text, we use the term ``spheroid'' to designate 
either a diskless elliptical galaxy or the bulge component of a disk galaxy, 
with no attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } and disk components of galaxies 
(e.g.~\citealt{caon1993,andredakis1995,iodice1997,iodice1999,seigar1998,khosroshahi2000}), 

@@

we performed state-of-the-art modelling for the largest sample of galaxies to date (Savorgnan \& Graham 2015a, hereafter \emph{Paper I}),  

@@

In Savorgnan et al.~(2015, hereafter \emph{Paper II}) we examined the correlations between the black hole mass and 
the total galaxy luminosity, the spheroid luminosity and the spheroid stellar mass. 

@@

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
Savorgnan \& Graham (2015b) demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices were estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by different studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes, which report only the statistical errors 
associated with their fitted parameters. 
Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as mergers are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
\label{sec:anal}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the lenticular galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis. 
{\bf quote fitexy results bcz more reliable than other 2 }
%I should have mentioned that the linear regression code, BCES, from Akritas & Bershady (1996) can at times get the slope wrong.  
%This occurs if the error bars on the velocity dispersion are too big relative to the range of velocity dispersions in one's sample (say >15%), 
%or if the error bars on the velocity dispersion and black hole masses are not all roughly the same. 
%That is, if some black hole masses have error bars of 50% while others have error bars of 5%, then we could be in trouble.

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001bulges}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{grahamworley2008} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{grahamworley2008} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
%It is also worth mentioning that, 
%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram using only our high-quality dataset. 
Spheroid luminositites and S\'ersic indices were obtained from accurate multicomponent decompositions,  
performed in a consistent manner using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{grahamworley2008} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
Early-type galaxies follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$; 
remarkably, this is exactly the same proportionality obtained by \cite{savorgnan2013} for elliptical galaxies only, 
upon re-analyzing the dataset from \cite{grahamguzman2003}. 
Late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations 
($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we find that 
early-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{3.58 \pm 0.27}$, 
while late-type galaxies follow $M_{\rm BH} \propto n_{\rm sph}^{4.55 \pm 0.66}$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph}^{\rm maj} - 0.50 \bigr) . 
\end{equation*}
\\
